Generating Images From Captions\\ With Attention

### 2015-11-01 iclr-paper-new.tex
a

\begin{figure}[!t]
\captionsetup[subfigure]{labelformat=empty}
\vspace{-0.3cm}
\begin{center}
\subfloat[A stop sign is flying in blue skies.
]{\includegraphics[width=0.23\textwidth]{figures/new/a-stop-sign-is-flying-in-blue-skies-sharp.png}}\quad
%
\subfloat[A herd of elephants flying in the blue skies.
]{\includegraphics[width=0.23\textwidth]{figures/new/a-herd-of-elephants-flying-in-the-blue-skies-sharp.png}}\quad
%
\subfloat[A toilet seat sits open in the grass field.
]{\includegraphics[width=0.23\textwidth]{figures/new/a-toilet-seat-sits-open-in-the-grass-field-sharp.png}}\quad
%
\subfloat[A person skiing on sand clad vast desert.
]{\includegraphics[width=0.23\textwidth]{figures/new/a-person-skiing-on-sand-clad-vast-desert-sharp.png}}\quad
%
\end{center}
\caption{Examples of novel scene compositions.}
\label{fig:genimages4}
\vspace{-0.3cm}
\end{figure}

@@

\begin{figure}[t!]
\captionsetup[subfigure]{labelformat=empty}
\begin{center}
\includegraphics[width=0.99\textwidth]{figures/alignDrawAnnotated.pdf}\quad
%
\end{center}
\caption{AlignDRAW model for generating images by learning an alignment between the input captions
and generating canvas. The caption is encoded using 
the Bidirectional RNN (left). The generative RNN takes a latent sequence $z_{1:T}$ sampled from the 
prior along with dynamic caption representation $s_{1:T}$ to generate the canvas matrix $c_T$, which is then
used to generate the final image $\oimage$ (right).
The inference RNN is used to compute approximate posterior $Q$ over the latent sequence.} 
\label{fig:figmodel}
\vspace{-0.3cm}
\end{figure}

@@

The $\decoder$ function of \Eqref{eq:decoder} 
is defined by the LSTM network with \textit{forget} gates 
\citep{gers_forget} at a single time-step. To generate the next 
hidden state $\hdec_t$, 
the $\decoder$ takes the previous hidden state $\hdec_{t-1}$ and
combines it with the input from both the latent sample $z_t$ and the sentence representation $s_t$.
%combines it with the input from both the latent sample $z_t$ and 
%sentence representation $s_t$, where
%$[v_1, v_2]$ denotes the concatenation of $v_1$ and $v_2$ into the single vector.

@@

\begin{figure}[!t]
\captionsetup[subfigure]{labelformat=empty}
\vspace{-0.3cm}
\begin{center}
\subfloat[A \underline{yellow} school bus parked in a parking lot.
]{\includegraphics[width=0.23\textwidth]{figures/new/a-yellow-school-bus-parked-in-a-parking-lot-sharp.png}}\quad
%
\subfloat[A \underline{red} school bus parked in a parking lot.
]{\includegraphics[width=0.23\textwidth]{figures/new/a-red-school-bus-parked-in-a-parking-lot-sharp.png}}\quad
%
\subfloat[A \underline{green} school bus parked in a parking lot.
]{\includegraphics[width=0.23\textwidth]{figures/new/a-green-school-bus-parked-in-a-parking-lot-sharp.png}}\quad
%
\subfloat[A \underline{blue} school bus parked in a parking lot.
]{\includegraphics[width=0.23\textwidth]{figures/new/a-blue-school-bus-parked-in-a-parking-lot-sharp.png}}\quad
\\
%
\subfloat[\underline{The decadent chocolate} \underline{desert} is on the table.
]{\includegraphics[width=0.23\textwidth]{figures/new/the-decadent-chocolate-dessert-is-on-the-table-sharp.png}}\quad
%
\subfloat[\underline{A bowl of bananas} is on the table.
]{\includegraphics[width=0.23\textwidth]{figures/new/a-bowl-of-bananas-is-on-the-table-sharp.png}}\quad
%
\subfloat[A vintage photo of a \underline{cat}.
]{\includegraphics[width=0.23\textwidth]{figures/new/a-vintage-photo-of-a-cat-sharp.png}}\quad
%
\subfloat[A vintage photo of a \underline{dog}.
]{\includegraphics[width=0.23\textwidth]{figures/new/a-vintage-photo-of-a-dog-sharp.png}}\quad
%
\end{center}
\caption{\textbf{Bottom}: Examples of changing the object while keeping the caption fixed. \textbf{Top}: Examples of changing the color while keeping the caption fixed.}
\label{fig:genimages3}
%\vspace{-0.3cm}
\end{figure}

@@

\begin{table}[!t]
\begin{center}
\begin{tabulary}{\linewidth}{c || c c c c c || c c}
\hline
\multicolumn{7}{c}{\textbf{Microsoft COCO (before sharpening)}} \\
\hline
& \multicolumn{5}{c||}{Image Search} & \multicolumn{1}{c}{Image Similarity} \\
%\cline{2-6}
\textbf{Model} & \textbf{R@1} & \textbf{R@5} & \textbf{R@10} & \textbf{R@50} & \textbf{Med r} & \textbf{SSI}\\ %& \textbf{Feature Distance} \\
\hline
\hline
LAPGAN & - & - & - & - & - & 0.08 \\ % & 6.89 \\ % - & - & - & - & - & 0.08
\hline
Fully-Conn VAE & 1.0 & 6.6 & 12.0 & 53.4 & 47 & 0.156 \\ %& 6.11 \\ % 0.688 & 4.58 & 8.74 & 46.832 & 54 & -1
Conv-Deconv VAE & 1.0 & 6.5 & 12.0 & 52.9 & 48 & 0.164 \\ %& 6.32 \\ % 0.672 & 4.448 & 8.476 & 46.596 & 54 & 0.131
skipthoughtDRAW & 2.0 & 11.2 & 18.9 & 63.3 & 36 & 0.157 \\ %& 6.93 \\ % 0.988 & 6.18 & 11.48 & 52.512 & 48 & 0.118
noalignDRAW & 2.8 & 14.1 & 23.1 & 68.0 & 31 & 0.155 \\ %& 7.01 \\ % 1.0 & 6.124 & 11.18 & 52.112 & 48 & 0.114
alignDRAW & 3.0 & 14.0 & 22.9 & 68.5 & 31 & 0.156 \\ %& 6.99 \\ % 0.924 & 6.216 & 11.184 & 52.492 & 48 & 0.115
\end{tabulary}
\end{center}
\caption{Results of different models.}
\label{tab:results}
%\vspace{-0.3cm}
\end{table}

>>>>

\begin{figure}[!t]
\captionsetup[subfigure]{labelformat=empty}
\vspace{-0.3cm}
\begin{center}
\subfloat[A stop sign is flying in blue skies.
]{\includegraphics[width=0.23\textwidth]{figures/new/a-stop-sign-is-flying-in-blue-skies-sharp.png}}\quad
%
\subfloat[A herd of elephants flying in the blue skies.
]{\includegraphics[width=0.23\textwidth]{figures/new/a-herd-of-elephants-flying-in-the-blue-skies-sharp.png}}\quad
%
\subfloat[A toilet seat sits open in the grass field.
]{\includegraphics[width=0.23\textwidth]{figures/new/a-toilet-seat-sits-open-in-the-grass-field-sharp.png}}\quad
%
\subfloat[A person skiing on sand clad vast desert.
]{\includegraphics[width=0.23\textwidth]{figures/new/a-person-skiing-on-sand-clad-vast-desert-sharp.png}}\quad
%
\end{center}
\caption{\small Examples of novel scene compositions.}
\label{fig:genimages4}
\vspace{-0.3cm}
\end{figure}

@@

\begin{figure}[t!]
\captionsetup[subfigure]{labelformat=empty}
\begin{center}
\includegraphics[width=0.99\textwidth]{figures/alignDrawAnnotated.pdf}\quad
%
\end{center}
\caption{\small AlignDRAW model for generating images by learning an alignment between the input captions
and generating canvas. The caption is encoded using 
the Bidirectional RNN (left). The generative RNN takes a latent sequence $z_{1:T}$ sampled from the 
prior along with dynamic caption representation $s_{1:T}$ to generate the canvas matrix $c_T$, which is then
used to generate the final image $\oimage$ (right).
The inference RNN is used to compute approximate posterior $Q$ over the latent sequence.} 
\label{fig:figmodel}
\vspace{-0.3cm}
\end{figure}

@@

The $\decoder$ function of \Eqref{eq:decoder} 
is defined by the LSTM network with \textit{forget} gates 
\citep{gers_forget} at a single time-step. To generate the next 
hidden state $\hdec_t$, 
the $\decoder$ takes the previous hidden state $\hdec_{t-1}$ and
combines it with the input from both the latent sample $z_t$ and 
sentence representation $s_t$, where
$[v_1, v_2]$ denotes the concatenation of $v_1$ and $v_2$ into the single vector.

@@

\begin{figure}[!t]
\captionsetup[subfigure]{labelformat=empty}
\vspace{-0.3cm}
\begin{center}
\subfloat[A \underline{yellow} school bus parked in a parking lot.
]{\includegraphics[width=0.23\textwidth]{figures/new/a-yellow-school-bus-parked-in-a-parking-lot-sharp.png}}\quad
%
\subfloat[A \underline{red} school bus parked in a parking lot.
]{\includegraphics[width=0.23\textwidth]{figures/new/a-red-school-bus-parked-in-a-parking-lot-sharp.png}}\quad
%
\subfloat[A \underline{green} school bus parked in a parking lot.
]{\includegraphics[width=0.23\textwidth]{figures/new/a-green-school-bus-parked-in-a-parking-lot-sharp.png}}\quad
%
\subfloat[A \underline{blue} school bus parked in a parking lot.
]{\includegraphics[width=0.23\textwidth]{figures/new/a-blue-school-bus-parked-in-a-parking-lot-sharp.png}}\quad
\\
%
\subfloat[\underline{The decadent chocolate} \underline{desert} is on the table.
]{\includegraphics[width=0.23\textwidth]{figures/new/the-decadent-chocolate-dessert-is-on-the-table-sharp.png}}\quad
%
\subfloat[\underline{A bowl of bananas} is on the table.
]{\includegraphics[width=0.23\textwidth]{figures/new/a-bowl-of-bananas-is-on-the-table-sharp.png}}\quad
%
\subfloat[A vintage photo of a \underline{cat}.
]{\includegraphics[width=0.23\textwidth]{figures/new/a-vintage-photo-of-a-cat-sharp.png}}\quad
%
\subfloat[A vintage photo of a \underline{dog}.
]{\includegraphics[width=0.23\textwidth]{figures/new/a-vintage-photo-of-a-dog-sharp.png}}\quad
%
\end{center}
\caption{\small \textbf{Bottom}: Examples of changing the object while keeping the caption fixed. \textbf{Top}: Examples of changing the color while keeping the caption fixed.}
\label{fig:genimages3}
%\vspace{-0.3cm}
\end{figure}

@@

\begin{table}[!t]
\begin{center}
\begin{tabulary}{\linewidth}{c || c c c c c || c c}
\hline
\multicolumn{7}{c}{\textbf{Microsoft COCO (before sharpening)}} \\
\hline
& \multicolumn{5}{c||}{Image Search} & \multicolumn{1}{c}{Image Similarity} \\
%\cline{2-6}
\textbf{Model} & \textbf{R@1} & \textbf{R@5} & \textbf{R@10} & \textbf{R@50} & \textbf{Med r} & \textbf{SSI}\\ %& \textbf{Feature Distance} \\
\hline
\hline
LAPGAN & - & - & - & - & - & 0.08 \\ % & 6.89 \\ % - & - & - & - & - & 0.08
\hline
Fully-Conn VAE & 1.0 & 6.6 & 12.0 & 53.4 & 47 & 0.156 \\ %& 6.11 \\ % 0.688 & 4.58 & 8.74 & 46.832 & 54 & -1
Conv-Deconv VAE & 1.0 & 6.5 & 12.0 & 52.9 & 48 & 0.164 \\ %& 6.32 \\ % 0.672 & 4.448 & 8.476 & 46.596 & 54 & 0.131
skipthoughtDRAW & 2.0 & 11.2 & 18.9 & 63.3 & 36 & 0.157 \\ %& 6.93 \\ % 0.988 & 6.18 & 11.48 & 52.512 & 48 & 0.118
noalignDRAW & 2.8 & 14.1 & 23.1 & 68.0 & 31 & 0.155 \\ %& 7.01 \\ % 1.0 & 6.124 & 11.18 & 52.112 & 48 & 0.114
alignDRAW & 3.0 & 14.0 & 22.9 & 68.5 & 31 & 0.156 \\ %& 6.99 \\ % 0.924 & 6.216 & 11.184 & 52.492 & 48 & 0.115
\end{tabulary}
\end{center}
\caption{Retrieval results of different models. \bf{ R$\at$K} is Recall@K (high is good). Med r is the median rank (low is good).
Best results overall are bold while best results without OxfordNet features are underlined}
\label{tab:results}
%\vspace{-0.3cm}
\end{table}
